\vspace{-2cm} Content of Municipal Government Websites

### 2017-04-05 paper/manuscript.tex
updated abstract

\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we apply an author-topic model [alternatively: structural topic model] to website data acquired from different points in time through the Wayback Machine.

>>>>

\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply the expressed agenda model (Grimmer 2010) to this corpus. This topic model allows us to identify which kinds of documents are prone to being modified, added and removed after transitions of power.
